Clicks and Cliques

### 2018-12-12 papersoul.Rnw
add weights mention

>>>>

Data from ACS are comunity variable, computed using sampling weights by Census Bureau. 
When using data from Knight Foundation surveys, the sampling weights need to be taken into
account, if thte data comes from only one year then the sampling weight is provided
in the data, when all three year survey data are used, sampling weights are divided by three 
so the total aggregate of each variable still can be consider an estimate of the comunity
total.
